\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{PS4\_Ryu}
\author{Junyeol Ryu}
\date{February 2024}

\begin{document}

\maketitle

\section{Kaggle}

Kaggle is a popular platform for data repository or data open source, offering several advantages for individuals and teams working in these fields:

\subsection{Competition}
Kaggle hosts various competitions, from beginner to advanced levels. In Kaggle, people can solve real-world problems, improve their visualization skills, and share some opinions and arguments. Even some participants win the prize. 

\subsection{Datasets}
Kaggle provides a various repository of datasets across various domains. This advantage make it easier for users to find and work with diverse data for their projects or research. 

\subsection{Community}
Kaggle has a large and active community of data scientists, economists, and scholars. Users can have discussions, ask questions, share insights, and learn from others' experiences. This advantage can build more collaborative learning environment.


\section{Answering the Question}
\subsection{Type of an object is mydf\$date?}
character

\subsection{List the first 3 rows of the mydf dataframe.}
1 1     Tiberius, under order of Augustus, quells revolts in Germania (1–5).         en    By pla… Roman … year   
\\
2 1     Gaius Caesar and Lucius Aemilius Paullus are appointed consuls.              en    By pla… Roman … year   
\\
3 1     Gaius Caesar marries Livilla, daughter of Antonia Minor and Nero Claudius D… en    By pla… Roman … year   

\end{document}
